Papers

### 2023-09-22 quarto/index.qmd
update

@@

* E. Grassucci, **A. Zhang**, and D. Comminiello<br>
	<a href="https://arxiv.org/abs/2110.04176" target="_blank">PHNNs: Lightweight Neural Networks via Parameterized Hypercomplex Convolutions</a><br>
	In *IEEE Transactions on Neural Networks and Learning Systems* (**TNNLS**), 2022<br>
	<a href="https://github.com/eleGAN23/HyperNets" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

>>>>

* Z. Zhang and **A. Zhang**<br>
<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
*"From screenshots to actions. It takes first principles thinking."*
In *arXiv*, 2023<br>
<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
<br>
<a href="https://arxiv.org/abs/2304.04704" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>
<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
<a href="https://arxiv.org/abs/2305.04241" target="_blank">Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>

@@

### 2023-09-22 quarto/papers.qmd
update

@@

* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
<br>
<a href="https://arxiv.org/abs/2304.04704" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
*"Scaling up prompt learning on ImageNet-21K achieves SOTA on 21 downstream datasets."*
In *arXiv*, 2023<br>
<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

@@

* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
<a href="https://arxiv.org/abs/2305.04241" target="_blank">Vcc: Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
*"Only a small subset of tokens are relevant to the output."*
In *arXiv*, 2023<br>

>>>>

* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
*"Can ChatGPT solve, for example, sequence tagging?"*
In *arXiv*, 2023<br>

* Z. Zhang and **A. Zhang**<br>
<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
*"From screenshots to actions. It takes first principles thinking."*
In *arXiv*, 2023<br>
<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* S. Ren, **A. Zhang**, Y. Zhu, S. Zhang, S. Zheng, M. Li, A. J. Smola, X. Sun
<br>
<a href="https://arxiv.org/abs/2304.04704" target="_blank">Prompt Pre-Training with Twenty-Thousand Classes for Open-Vocabulary Visual Recognition</a><br>
In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>
<a href="https://github.com/amazon-science/prompt-pretraining" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
<a href="https://arxiv.org/abs/2305.04241" target="_blank">Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
In *Proceedings of the Conference on Neural Information Processing Systems* (**NeurIPS**), 2023<br>

@@

@@
